Inferring the gravitational potential of the Milky Way with few precisely measured stars

### 2014-02-01 text/paper2/ms.tex

Things to address:
- Density is hard to match -- need background model, way to go from luminosity to density, needs assumptions about the mass function and structure of the satellite
-

@@

\pagebreak

(Hogg comments)

[Generalization to multiple phase-space structures. Mixture of
  mixtures.]

[Comment on bow-tie structure, Kuepper work, and so on;
  might want to generalize the Gaussian brutality.]

\section{Tests on simulated data}

[Each experiment requires a description of how the fake data were
  generated, what the likelihood function is, and posterior potential
  information obtained.]

\subsection{\gaia + \spitzer}

\subsection{\spitzer + current data}

@@

@@

[Don't be afraid of nuisance parameters!]

>>>>

[Densities are hard to match -- need a background model, way to go from luminosity to density, needs assumptions about the mass function and structure of the satellite\

[Cold vs. Hot streams in the context of observational errors]

[We properly handle observational errors]

@@

\subsection{\gaia + \spitzer}
64 stars in Sgr-like stream

\subsection{\spitzer + current data}
64 stars in Sgr-like stream

\subsection{\spitzer + current data, no progenitor}
32 stars in Orphan-like stream, XX stars in GD-1 -like stream

@@

[Cold vs. Hot streams]

[bow-tie structure, Kuepper work, and so on]

@@
